%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Intelligent Machines Ltd.} % Organization
    {Dhaka, Bangladesh} % Location
    {Mar 2021-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built fully automated CI/CD pipelines for containerized NodeJs applications using Docker and Azure CR.}
        \item {Designed an overall service architecture and pipelines of a MERN stack product with the micro-services architecture.}
        \item {Implemented several API microservices in Nodejs.}
        \item {Implemented a data pipeline among multiple AI and Analytics servers with a message broker system in RabbitMQ.}
        \item {Developed a responsive web application in ReactJs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer (L2)} % Job title
    {Field Information Solutions Ltd.} % Organization
    {Dhaka, Bangladesh} % Location
    {Jul 2019-Mar 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed features for the Field Buzz Android libraries and implemented SaaS modules of the Field Buzz Sales system.}
        \item {Implemented several last mile field operation features (Java, Android SDK) that include Geo mapping, retailer shop management, loan collection, inventory management, surveys, report generation, etc.}
        \item {Worked as the lead developer for Microfinance mobile apps (Java, Android SDK, Realm, Django) that digitize and analyze credit procedures in the field, from member registration to loan repayments.}
        % \item {Worked on the Brazil, Uganda, Kenya, and Honduras field management mobile apps of Neumann Kaffee Gruppe.}
        \item {Worked on an intelligent mobile sync engine (Android SDK, CI/CD with Jenkins) that works with unreliable or no internet.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Job title
    {Durbin Labs Ltd.} % Organization
    {Dhaka, Bangladesh} % Location
    {May 2016-Jan 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as an intern on the mobile team during the undergrad years.}
        \item {Learned android development, back-end development, design patterns, writing API.}
        \item {Implemented the UI of the Grameenphone MyStudy app.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
